draft_final_assignment

### 2022-11-29 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

summary_sentiment <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_w_vader.csv")
```
```{r}
ggplot(summary_sentiment, aes(x = compound)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="white") +
  geom_density(alpha=.1, fill="blue") +
  labs(title="Density of compount sentiment scores",
       x ="Sentiment scores", y = "Density") +
  theme_minimal()
```

>>>>

summary_sentiment <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_w_vader.csv")
```
```{r}
ggplot(summary_sentiment, aes(x = compound)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="white") +
  geom_density(alpha=.1, fill="blue") +
  labs(title="Density of compound sentiment scores",
       x ="Sentiment scores", y = "Density") +
  theme_minimal()
```
